### 2020-07-02 evaluation.tex
change reallife fig

\subsection{Comparison with other architectures}
We train and test other commonly used architectures with the same sets of data and evaluate their results. We chose SRCNN, a commonly used single image SR network, and applied it to each single image before merging the results by pixel-level average. We also used a multi-frame version of CNN consisting of 3D convolutional layers, designed for video super resolution (VideoSR). However, as mentioned above, it is very difficult for the single image approaches to utilize information and distinguish the noisy and deformed patterns, while VideoSR approaches rely upon consistency between frames, so they fail to give satisfactory results. We used the relatively easy 'daytime 1.2m-distance direct with traditional lens' group of data for testing. The results are shown in Table~\ref{table-comp}.
\begin{table}[!t]
    \centering
    \caption{Comparison with existing systems.}
    \begin{tabular}{@{}cccc@{}}
        \toprule
    System & SRPeek & SRCNN & VideoSR \\ \midrule
    PSNR(db) & 13.32 & 7.69 & 8.403\\ 
    OCR Accuracy(\%) & 100 & 10 & 23\\ \bottomrule
    \end{tabular}
    \label{table-comp}
\end{table}

@@

We build the system on smartphone and evaluate its performance in real-life environments (shown in Fig.~\ref{fig-reallife}). We experiment with a Redmi 6A smartphone (with a camera of 13 million pixels) for the attacker and a HUAWEI Mate8 smartphone for the victim. As the telephoto cameras can assist the attacker to see clearly at approximately 3m distance without any aid from SR algorithms, we believe it is insignificant to further extend this distance to judge it as a threat to privacy, so that the following experiments are performed with traditional lens at 1-2m range. We ask 5 human participants to read the reconstructed characters to evaluate the usability of our model. No participants can read the unprocessed images, but all of them can decipher the information on the reconstructed image without much difficulty. The results are shown in Table~\ref{table-scenarios}.
\begin{figure}
	\centering
	\includegraphics[width=0.48\textwidth]{pic/reallife.jpg}
    \caption{Illustration of our real-life scenario (Distance between attacker and victim is shortened for demonstration).}
	\label{fig-reallife}
\end{figure}

@@

\begin{table}[!t]
    \centering
    \caption{Recognition accuracy in various scenarios.}
    \begin{tabular}{@{}cccc@{}}
        \toprule
    Scenarios & Home & Transport & Theater \\ \midrule
    Baseline & 5 & 0 & 0\\ 
    \midrule
    OCR & 100 & 10 & 23\\ 
    Human & 95 & 85 & 70\\ \bottomrule
    \end{tabular}
    \label{table-scenarios}
\end{table}

@@

\begin{table}[!t] 
    \centering
    \caption{Impact of hand tremors when the camera(attacker phone) and/or target(victim phone) is handheld.}
    \begin{tabular}{ccccc}
        \toprule
    Items & None & Camera & Target & Both  \\
    \midrule
    Baseline & 5 & 0 & 5& 5\\ 
    \midrule
    OCR & 95 & 85 & 80 & 80\\ 
    Human & 95 & 85 & 80 & 85\\ \bottomrule
    \end{tabular}
    \label{table-tremor}
\end{table}

@@

\begin{table}[!t]
\centering
\caption{Success rate in different tasks.}
\label{table-task}
\begin{tabular}{@{}ccccc@{}}
	\toprule
Accuracy & Read text & Type text & Enter PIN & Enter password\\ \midrule
Raw Image & 5 & 0 & 0 & 0\\
SRPeek & 100 & 100 & 100 & 80\\ \bottomrule
\end{tabular}

>>>>

\subsection{Comparison with other architectures}
We train and test other commonly used architectures with the same sets of data and evaluate their results. We chose SRCNN, a commonly used single image SR network, and applied it to each single image before merging the results by pixel-level average. We also used a multi-frame version of CNN consisting of 3D convolutional layers, designed for video super resolution (VideoSR). However, as mentioned above, it is very difficult for the single image approaches to utilize information and distinguish the noisy and deformed patterns, while VideoSR approaches rely upon consistency between frames, so they fail to give satisfactory results. We used the relatively easy 'daytime 1.2m-distance direct with traditional lens' group of data for testing. The results are shown in Table~\ref{table-comp}.
\begin{table}[!t]
    \centering
    \caption{Comparison with existing systems.}
    \begin{tabular}{@{}cccc@{}}
        \toprule
    System & SRPeek & SRCNN & VideoSR \\ \midrule
    PSNR & 13.32db & 7.69db & 8.403db\\ 
    OCR Accuracy & 100\% & 10\% & 23\%\\ \bottomrule
    \end{tabular}
    \label{table-comp}
\end{table}

@@

We build the system on smartphone and evaluate its performance in real-life environments (shown in Fig.~\ref{fig-reallife}). We experiment with a Redmi 6A smartphone (with a camera of 13 million pixels) for the attacker and a HUAWEI Mate8 smartphone for the victim. As the telephoto cameras can assist the attacker to see clearly at approximately 3m distance without any aid from SR algorithms, we believe it is insignificant to further extend this distance to judge it as a threat to privacy, so that the following experiments are performed with traditional lens at 1-2m range. We ask 5 human participants to read the reconstructed characters to evaluate the usability of our model. No participants can read the unprocessed images, but all of them can decipher the information on the reconstructed image without much difficulty. The results are shown in Table~\ref{table-scenarios}.
\begin{figure}
	\centering
	\includegraphics[width=0.46\textwidth]{pic/reallife.pdf}
    \caption{Illustration of our real-life scenario (Distance between attacker and victim is shortened for demonstration).}
	\label{fig-reallife}
\end{figure}

@@

\begin{table}[!t]
    \centering
    \caption{Recognition accuracy in various scenarios.}
    \begin{tabular}{@{}cccc@{}}
        \toprule
    Scenarios & Home & Transport & Theater \\ \midrule
    Baseline & 5\% & 0 & 0\\ 
    \midrule
    OCR & 100\% & 10\% & 23\%\\ 
    Human & 95\% & 85\% & 70\%\\ \bottomrule
    \end{tabular}
    \label{table-scenarios}
\end{table}

@@

\begin{table}[!t] 
    \centering
    \caption{Impact of hand tremors when the camera (attacker phone) and/or target (victim phone) is handheld.}
    \begin{tabular}{ccccc}
        \toprule
    Accuracy & None & Camera & Target & Both  \\
    \midrule
    Baseline & 5\% & 0 & 5\% & 5\%\\ 
    \midrule
    OCR & 95\% & 85\% & 80\% & 80\%\\ 
    Human & 95\% & 85\% & 80\% & 85\%\\ \bottomrule
    \end{tabular}
    \label{table-tremor}
\end{table}

@@

\begin{table}[!t]
\centering
\caption{Success rate in different tasks.}
\label{table-task}
\begin{tabular}{@{}ccccc@{}}
	\toprule
Accuracy & Read text & Type text & Enter PIN & Enter password\\ \midrule
Raw Image & 5\% & 0 & 0 & 0\\
SRPeek & 100\% & 100\% & 100\% & 80\%\\ \bottomrule
\end{tabular}
